The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2013-05-01 ms.tex
Update ms.tex
updated ms.tex file contents

@@

The survey has detected approximately \ncoresapprox\ clumps over the
entire area to a limiting non-uniform 1-$\sigma$ noise level in the
range \bgpsdepthlow\ to \bgpsdepthhigh\ m\jyb\ in the inner Galaxy.
The BGPS source catalog is presented in a companion paper
\citep{rosolowsky10}.  This paper details the survey observations and
data reduction methods for the images.  We discuss in detail the
determination of astrometric and flux density calibration
uncertainties and compare our results to the literature.  Data
processing algorithms that separate astronomical signals from
time-variable atmospheric fluctuations in the data time-stream are
presented.  These algorithms reproduce the structure of the
astronomical sky over a limited range of angular scales and produce
artifacts in the vicinity of bright sources. Based on simulations, we
find that extended emission on scales larger than about 5\farcm9 is
nearly completely attenuated ($>90\%$) and the linear scale at which
the attenuation reaches 50\% is 3\farcm8.  Comparison with other
millimeter-wave data sets implies a possible systematic offset in flux
calibration, for which no cause has been discovered.

@@

\begin{thebibliography}{61}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Bally} {et~al.}(2010){Bally}, {Aguirre}, {Battersby}, {Bradley},
  {Cyganowski}, {Dowell}, {Drosback}, {Dunham}, {Evans}, {Ginsburg}, {Glenn},
  {Harvey}, {Mills}, {Merello}, {Rosolowsky}, {Schlingman}, {Shirley},
  {Stringfellow}, {Walawender}, \& {Williams}}]{bally10}
{Bally}, J. {et~al.} 2010, \apj, 721, 137

\bibitem[{{Battersby} {et~al.}(2010){Battersby}, {Bally}, {Jackson},
  {Ginsburg}, {Shirley}, {Schlingman}, \& {Glenn}}]{battersby10}
{Battersby}, C., {Bally}, J., {Jackson}, J.~M., {Ginsburg}, A., {Shirley},
  Y.~L., {Schlingman}, W., \& {Glenn}, J. 2010, \apj, 721, 222

\bibitem[{{Benjamin} {et~al.}(2003){Benjamin}, {Churchwell}, {Babler}, {Bania},
  {Clemens}, {Cohen}, {Dickey}, {Indebetouw}, {Jackson}, {Kobulnicky},
  {Lazarian}, {Marston}, {Mathis}, {Meade}, {Seager}, {Stolovy}, {Watson},
  {Whitney}, {Wolff}, \& {Wolfire}}]{benjamin03}
{Benjamin}, R.~A. {et~al.} 2003, \pasp, 115, 953

\bibitem[{{Beuther} {et~al.}(2004){Beuther}, {Zhang}, {Greenhill}, {Reid},
  {Wilner}, {Keto}, {Marrone}, {Ho}, {Moran}, {Rao}, {Shinnaga}, \&
  {Liu}}]{beuther04}
{Beuther}, H. {et~al.} 2004, \apjl, 616, L31

\bibitem[{{Buckle} {et~al.}(2009){Buckle}, {Hills}, {Smith}, {Dent}, {Bell},
  {Curtis}, {Dace}, {Gibson}, {Graves}, {Leech}, {Richer}, {Williamson},
  {Withington}, {Yassin}, {Bennett}, {Hastings}, {Laidlaw}, {Lightfoot},
  {Burgess}, {Dewdney}, {Hovey}, {Willis}, {Redman}, {Wooff}, {Berry},
  {Cavanagh}, {Davis}, {Dempsey}, {Friberg}, {Jenness}, {Kackley}, {Rees},
  {Tilanus}, {Walther}, {Zwart}, {Klapwijk}, {Kroug}, \& {Zijlstra}}]{buckle09}
{Buckle}, J.~V. {et~al.} 2009, \mnras, 399, 1026

\bibitem[{{Carey} {et~al.}(1998){Carey}, {Clark}, {Egan}, {Price}, {Shipman},
  \& {Kuchar}}]{carey98}
{Carey}, S.~J., {Clark}, F.~O., {Egan}, M.~P., {Price}, S.~D., {Shipman},
  R.~F., \& {Kuchar}, T.~A. 1998, \apj, 508, 721

\bibitem[{{Carey} {et~al.}(2009){Carey}, {Noriega-Crespo}, {Mizuno}, {Shenoy},
  {Paladini}, {Kraemer}, {Price}, {Flagey}, {Ryan}, {Ingalls}, {Kuchar},
  {Pinheiro Gon{\c c}alves}, {Indebetouw}, {Billot}, {Marleau}, {Padgett},
  {Rebull}, {Bressert}, {Ali}, {Molinari}, {Martin}, {Berriman}, {Boulanger},
  {Latter}, {Miville-Deschenes}, {Shipman}, \& {Testi}}]{carey09}
{Carey}, S.~J. {et~al.} 2009, \pasp, 121, 76

\bibitem[{{Chapin} {et~al.}(2008){Chapin}, {Ade}, {Bock}, {Brunt}, {Devlin},
  {Dicker}, {Griffin}, {Gundersen}, {Halpern}, {Hargrave}, {Hughes}, {Klein},
  {Marsden}, {Martin}, {Mauskopf}, {Netterfield}, {Olmi}, {Pascale},
  {Patanchon}, {Rex}, {Scott}, {Semisch}, {Truch}, {Tucker}, {Tucker}, {Viero},
  \& {Wiebe}}]{chapin08}
{Chapin}, E.~L. {et~al.} 2008, \apj, 681, 428

\bibitem[{{Cotton} {et~al.}(2009){Cotton}, {Mason}, {Dicker}, {Korngut},
  {Devlin}, {Aquirre}, {Benford}, {Moseley}, {Staguhn}, {Irwin}, \&
  {Ade}}]{cotton09}
{Cotton}, W.~D. {et~al.} 2009, \apj, 701, 1872

\bibitem[{{Cyganowski} {et~al.}(2007){Cyganowski}, {Brogan}, \&
  {Hunter}}]{cyganowski07}
{Cyganowski}, C.~J., {Brogan}, C.~L., \& {Hunter}, T.~R. 2007, \aj, 134, 346

\bibitem[{{Dame} {et~al.}(2001){Dame}, {Hartmann}, \& {Thaddeus}}]{dame01}
{Dame}, T.~M., {Hartmann}, D., \& {Thaddeus}, P. 2001, \apj, 547, 792

\bibitem[{{Di Francesco}(2008)}]{difrancesco08b}
{Di Francesco}, J. 2008, in Bulletin of the American Astronomical Society,
  Vol.~40, Bulletin of the American Astronomical Society, 271--+

\bibitem[{{Di Francesco} {et~al.}(2008){Di Francesco}, {Johnstone}, {Kirk},
  {MacKenzie}, \& {Ledwosinska}}]{difrancesco08}
{Di Francesco}, J., {Johnstone}, D., {Kirk}, H., {MacKenzie}, T., \&
  {Ledwosinska}, E. 2008, \apjs, 175, 277

\bibitem[{{Dunham} {et~al.}(2010){Dunham}, {Rosolowsky}, {Evans}, {Cyganowski},
  {Aguirre}, {Bally}, {Battersby}, {Bradley}, {Dowell}, {Drosback}, {Ginsburg},
  {Glenn}, {Harvey}, {Merello}, {Schlingman}, {Shirley}, {Stringfellow},
  {Walawender}, \& {Williams}}]{dunham10}
{Dunham}, M.~K. {et~al.} 2010, \apj, 717, 1157

\bibitem[{{Egan} {et~al.}(1998){Egan}, {Shipman}, {Price}, {Carey}, {Clark}, \&
  {Cohen}}]{egan98}
{Egan}, M.~P., {Shipman}, R.~F., {Price}, S.~D., {Carey}, S.~J., {Clark},
  F.~O., \& {Cohen}, M. 1998, \apjl, 494, L199+

\bibitem[{{Enoch} {et~al.}(2008){Enoch}, {Evans}, {Sargent}, {Glenn},
  {Rosolowsky}, \& {Myers}}]{enoch08}
{Enoch}, M.~L., {Evans}, II, N.~J., {Sargent}, A.~I., {Glenn}, J.,
  {Rosolowsky}, E., \& {Myers}, P. 2008, \apj, 684, 1240

\bibitem[{{Enoch} {et~al.}(2007){Enoch}, {Glenn}, {Evans}, {Sargent}, {Young},
  \& {Huard}}]{enoch07}
{Enoch}, M.~L., {Glenn}, J., {Evans}, II, N.~J., {Sargent}, A.~I., {Young},
  K.~E., \& {Huard}, T.~L. 2007, \apj, 666, 982

\bibitem[{{Enoch} {et~al.}(2006){Enoch}, {Young}, {Glenn}, {Evans}, {Golwala},
  {Sargent}, {Harvey}, {Aguirre}, {Goldin}, {Haig}, {Huard}, {Lange},
  {Laurent}, {Maloney}, {Mauskopf}, {Rossinot}, \& {Sayers}}]{enoch06}
{Enoch}, M.~L. {et~al.} 2006, \apj, 638, 293

\bibitem[{{Evans} {et~al.}(2009){Evans}, {Dunham}, {J{\o}rgensen}, {Enoch},
  {Mer{\'{\i}}n}, {van Dishoeck}, {Alcal{\'a}}, {Myers}, {Stapelfeldt},
  {Huard}, {Allen}, {Harvey}, {van Kempen}, {Blake}, {Koerner}, {Mundy},
  {Padgett}, \& {Sargent}}]{evans09}
{Evans}, N.~J. {et~al.} 2009, \apjs, 181, 321

\bibitem[{{Glenn} {et~al.}(2003){Glenn}, {Ade}, {Amarie}, {Bock}, {Edgington},
  {Goldin}, {Golwala}, {Haig}, {Lange}, {Laurent}, {Mauskopf}, {Yun}, \&
  {Nguyen}}]{glenn03}
{Glenn}, J. {et~al.} 2003, in \procspie, Vol. 4855, Millimeter and
  Submillimeter Detectors for Astronomy, 30

\bibitem[{{Griffin} \& {Orton}(1993)}]{griffin93}
{Griffin}, M.~J. \& {Orton}, G.~S. 1993, Icarus, 105, 537

\bibitem[{{Holland} {et~al.}(1999){Holland}, {Robson}, {Gear}, {Cunningham},
  {Lightfoot}, {Jenness}, {Ivison}, {Stevens}, {Ade}, {Griffin}, {Duncan},
  {Murphy}, \& {Naylor}}]{holland99}
{Holland}, W.~S. {et~al.} 1999, \mnras, 303, 659

\bibitem[{{Hollis} {et~al.}(1992){Hollis}, {Dorband}, \&
  {Yusef-Zadeh}}]{hollis92}
{Hollis}, J.~M., {Dorband}, J.~E., \& {Yusef-Zadeh}, F. 1992, \apj, 386, 293

\bibitem[{{Jackson} {et~al.}(2006){Jackson}, {Rathborne}, {Shah}, {Simon},
  {Bania}, {Clemens}, {Chambers}, {Johnson}, {Dormody}, {Lavoie}, \&
  {Heyer}}]{jackson06}
{Jackson}, J.~M. {et~al.} 2006, \apjs, 163, 145

\bibitem[{{Johnstone} \& {Bally}(1999)}]{johnstone99}
{Johnstone}, D. \& {Bally}, J. 1999, \apjl, 510, L49

\bibitem[{{Johnstone} \& {Bally}(2006)}]{johnstone06}
---. 2006, \apj, 653, 383

\bibitem[{{Kauffmann} {et~al.}(2008){Kauffmann}, {Bertoldi}, {Bourke}, {Evans},
  \& {Lee}}]{kauffmann08}
{Kauffmann}, J., {Bertoldi}, F., {Bourke}, T.~L., {Evans}, II, N.~J., \& {Lee},
  C.~W. 2008, \aap, 487, 993

\bibitem[{{Kov{\'a}cs}(2008)}]{kovacs08}
{Kov{\'a}cs}, A. 2008, in Presented at the Society of Photo-Optical
  Instrumentation Engineers (SPIE) Conference, Vol. 7020, Society of
  Photo-Optical Instrumentation Engineers (SPIE) Conference Series

\bibitem[{{Lada} {et~al.}(1991){Lada}, {Bally}, \& {Stark}}]{lada91}
{Lada}, E.~A., {Bally}, J., \& {Stark}, A.~A. 1991, \apj, 368, 432

\bibitem[{{Laurent} {et~al.}(2005){Laurent}, {Aguirre}, {Glenn}, {Ade}, {Bock},
  {Edgington}, {Goldin}, {Golwala}, {Haig}, {Lange}, {Maloney}, {Mauskopf},
  {Nguyen}, {Rossinot}, {Sayers}, \& {Stover}}]{laurent05}
{Laurent}, G.~T. {et~al.} 2005, \apj, 623, 742

\bibitem[{{Matthews} {et~al.}(2009){Matthews}, {Kirk}, {Johnstone},
  {Weferling}, {Cohen}, {Jenness}, {Evans}, {Davis}, {Dent}, {Fuller},
  {Jackson}, {Rathborne}, {Richer}, \& {Simon}}]{matthews09}
{Matthews}, H. {et~al.} 2009, \aj, 138, 1380

\bibitem[{{McKee} \& {Ostriker}(2007)}]{mckee07}
{McKee}, C.~F. \& {Ostriker}, E.~C. 2007, \araa, 45, 565

\bibitem[{{Molinari} {et~al.}(2010){Molinari}, {Swinyard}, {Bally}, {Barlow},
  {Bernard}, {Martin}, {Moore}, {Noriega-Crespo}, {Plume}, {Testi}, {Zavagno},
  {Abergel}, {Ali}, {Andr{\'e}}, {Baluteau}, {Benedettini}, {Bern{\'e}},
  {Billot}, {Blommaert}, {Bontemps}, {Boulanger}, {Brand}, {Brunt}, {Burton},
  {Campeggio}, {Carey}, {Caselli}, {Cesaroni}, {Cernicharo}, {Chakrabarti},
  {Chrysostomou}, {Codella}, {Cohen}, {Compiegne}, {Davis}, {de Bernardis}, {de
  Gasperis}, {Di Francesco}, {di Giorgio}, {Elia}, {Faustini}, {Fischera},
  {Fukui}, {Fuller}, {Ganga}, {Garcia-Lario}, {Giard}, {Giardino}, {Glenn},
  {Goldsmith}, {Griffin}, {Hoare}, {Huang}, {Jiang}, {Joblin}, {Joncas},
  {Juvela}, {Kirk}, {Lagache}, {Li}, {Lim}, {Lord}, {Lucas}, {Maiolo},
  {Marengo}, {Marshall}, {Masi}, {Massi}, {Matsuura}, {Meny}, {Minier},
  {Miville-Desch{\^e}nes}, {Montier}, {Motte}, {M{\"u}ller}, {Natoli}, {Neves},
  {Olmi}, {Paladini}, {Paradis}, {Pestalozzi}, {Pezzuto}, {Piacentini},
  {Pomar{\`e}s}, {Popescu}, {Reach}, {Richer}, {Ristorcelli}, {Roy}, {Royer},
  {Russeil}, {Saraceno}, {Sauvage}, {Schilke}, {Schneider-Bontemps},
  {Schuller}, {Schultz}, {Shepherd}, {Sibthorpe}, {Smith}, {Smith},
  {Spinoglio}, {Stamatellos}, {Strafella}, {Stringfellow}, {Sturm}, {Taylor},
  {Thompson}, {Tuffs}, {Umana}, {Valenziano}, {Vavrek}, {Viti}, {Waelkens},
  {Ward-Thompson}, {White}, {Wyrowski}, {Yorke}, \& {Zhang}}]{molinari10}
{Molinari}, S. {et~al.} 2010, \pasp, 122, 314

\bibitem[{{Motte} \& {Andr{\'e}}(2001)}]{motte01}
{Motte}, F. \& {Andr{\'e}}, P. 2001, \aap, 365, 440

\bibitem[{{Motte} {et~al.}(2007){Motte}, {Bontemps}, {Schilke}, {Schneider},
  {Menten}, \& {Brogui{\`e}re}}]{motte07}
{Motte}, F., {Bontemps}, S., {Schilke}, P., {Schneider}, N., {Menten}, K.~M.,
  \& {Brogui{\`e}re}, D. 2007, \aap, 476, 1243

\bibitem[{{Mueller} {et~al.}(2002){Mueller}, {Shirley}, {Evans}, \&
  {Jacobson}}]{mueller02}
{Mueller}, K.~E., {Shirley}, Y.~L., {Evans}, II, N.~J., \& {Jacobson}, H.~R.
  2002, \apjs, 143, 469

\bibitem[{{Netterfield} {et~al.}(2009){Netterfield}, {Ade}, {Bock}, {Chapin},
  {Devlin}, {Griffin}, {Gundersen}, {Halpern}, {Hargrave}, {Hughes}, {Klein},
  {Marsden}, {Martin}, {Mauskopf}, {Olmi}, {Pascale}, {Patanchon}, {Rex},
  {Roy}, {Scott}, {Semisch}, {Thomas}, {Truch}, {Tucker}, {Tucker}, {Viero}, \&
  {Wiebe}}]{netterfield09}
{Netterfield}, C.~B. {et~al.} 2009, \apj, 707, 1824

\bibitem[{{Nummelin} {et~al.}(1998){Nummelin}, {Bergman}, {Hjalmarson},
  {Friberg}, {Irvine}, {Millar}, {Ohishi}, \& {Saito}}]{nummelin1998}
{Nummelin}, A., {Bergman}, P., {Hjalmarson}, A., {Friberg}, P., {Irvine},
  W.~M., {Millar}, T.~J., {Ohishi}, M., \& {Saito}, S. 1998, \apjs, 117, 427

\bibitem[{{Olmi} {et~al.}(2009){Olmi}, {Ade}, {Angl{\'e}s-Alc{\'a}zar}, {Bock},
  {Chapin}, {De Luca}, {Devlin}, {Dicker}, {Elia}, {Fazio}, {Giannini},
  {Griffin}, {Gundersen}, {Halpern}, {Hargrave}, {Hughes}, {Klein},
  {Lorenzetti}, {Marengo}, {Marsden}, {Martin}, {Massi}, {Mauskopf},
  {Netterfield}, {Patanchon}, {Rex}, {Salama}, {Scott}, {Semisch}, {Smith},
  {Strafella}, {Thomas}, {Truch}, {Tucker}, {Tucker}, {Viero}, \&
  {Wiebe}}]{olmi09}
{Olmi}, L. {et~al.} 2009, \apj, 707, 1836

\bibitem[{{Orton} {et~al.}(1986){Orton}, {Griffin}, {Ade}, {Nolt}, \&
  {Radostitz}}]{orton86}
{Orton}, G.~S., {Griffin}, M.~J., {Ade}, P.~A.~R., {Nolt}, I.~G., \&
  {Radostitz}, J.~V. 1986, Icarus, 67, 289

\bibitem[{{Ossenkopf} \& {Henning}(1994)}]{ossenkopf94}
{Ossenkopf}, V. \& {Henning}, T. 1994, \aap, 291, 943

\bibitem[{{Peretto} \& {Fuller}(2009)}]{peretto09}
{Peretto}, N. \& {Fuller}, G.~A. 2009, \aap, 505, 405

\bibitem[{{Pohl} {et~al.}(2008){Pohl}, {Englmaier}, \&
  {Bissantz}}]{RotationCurve}
{Pohl}, M., {Englmaier}, P., \& {Bissantz}, N. 2008, \apj, 677, 283

\bibitem[{{Rathborne} {et~al.}(2006){Rathborne}, {Jackson}, \&
  {Simon}}]{rathborne06}
{Rathborne}, J.~M., {Jackson}, J.~M., \& {Simon}, R. 2006, \apj, 641, 389

\bibitem[{{Rathborne} {et~al.}(2008){Rathborne}, {Jackson}, {Zhang}, \&
  {Simon}}]{rathborne08}
{Rathborne}, J.~M., {Jackson}, J.~M., {Zhang}, Q., \& {Simon}, R. 2008, \apj,
  689, 1141

\bibitem[{{Reach} {et~al.}(1995){Reach}, {Dwek}, {Fixsen}, {Hewagama},
  {Mather}, {Shafer}, {Banday}, {Bennett}, {Cheng}, {Eplee}, {Leisawitz},
  {Lubin}, {Read}, {Rosen}, {Shuman}, {Smoot}, {Sodroski}, \&
  {Wright}}]{reach95}
{Reach}, W.~T. {et~al.} 1995, \apj, 451, 188

\bibitem[{{Reid} {et~al.}(2009){Reid}, {Menten}, {Zheng}, {Brunthaler},
  {Moscadelli}, {Xu}, {Zhang}, {Sato}, {Honma}, {Hirota}, {Hachisuka}, {Choi},
  {Moellenbrock}, \& {Bartkiewicz}}]{reid09}
{Reid}, M.~J. {et~al.} 2009, \apj, 700, 137

\bibitem[{{Rosolowsky} {et~al.}(2010){Rosolowsky}, {Dunham}, {Ginsburg},
  {Bradley}, {Aguirre}, {Bally}, {Battersby}, {Cyganowski}, {Dowell},
  {Drosback}, {Evans}, {Glenn}, {Harvey}, {Stringfellow}, {Walawender}, \&
  {Williams}}]{rosolowsky10}
{Rosolowsky}, E. {et~al.} 2010, \apjs, 188, 123

\bibitem[{{Roy} {et~al.}(2010){Roy}, {Ade}, {Bock}, {Chapin}, {Devlin},
  {Dicker}, {Griffin}, {Gundersen}, {Halpern}, {Hargrave}, {Hughes}, {Klein},
  {Marsden}, {Martin}, {Mauskopf}, {Miville-Desch{\^e}nes}, {Netterfield},
  {Olmi}, {Patanchon}, {Rex}, {Scott}, {Semisch}, {Truch}, {Tucker}, {Tucker},
  {Viero}, \& {Wiebe}}]{roy10}
{Roy}, A. {et~al.} 2010, \apj, 708, 1611

\bibitem[{{Sayers} {et~al.}(2010){Sayers}, {Golwala}, {Ade}, {Aguirre}, {Bock},
  {Edgington}, {Glenn}, {Goldin}, {Haig}, {Lange}, {Laurent}, {Mauskopf},
  {Nguyen}, {Rossinot}, \& {Schlaerth}}]{sayers10}
{Sayers}, J. {et~al.} 2010, \apj, 708, 1674

\bibitem[{{Sayers} {et~al.}(2009){Sayers}, {Golwala}, {Rossinot}, {Ade},
  {Aguirre}, {Bock}, {Edgington}, {Glenn}, {Goldin}, {Haig}, {Lange},
  {Laurent}, {Mauskopf}, \& {Nguyen}}]{sayers09}
---. 2009, \apj, 690, 1597

\bibitem[{{Schlingman} {et~al.}(2010)}]{schlingman10}
{Schlingman}, W. {et~al.} 2010, \apj, in prep

\bibitem[{{Schuller} {et~al.}(2009){Schuller}, {Menten}, {Contreras},
  {Wyrowski}, {Schilke}, {Bronfman}, {Henning}, {Walmsley}, {Beuther},
  {Bontemps}, {Cesaroni}, {Deharveng}, {Garay}, {Herpin}, {Lefloch}, {Linz},
  {Mardones}, {Minier}, {Molinari}, {Motte}, {Nyman}, {Reveret}, {Risacher},
  {Russeil}, {Schneider}, {Testi}, {Troost}, {Vasyunina}, {Wienen}, {Zavagno},
  {Kovacs}, {Kreysa}, {Siringo}, \& {Wei{\ss}}}]{schuller09}
{Schuller}, F. {et~al.} 2009, \aap, 504, 415

\bibitem[{{Simon} {et~al.}(2006{\natexlab{a}}){Simon}, {Jackson}, {Rathborne},
  \& {Chambers}}]{simon06a}
{Simon}, R., {Jackson}, J.~M., {Rathborne}, J.~M., \& {Chambers}, E.~T.
  2006{\natexlab{a}}, \apj, 639, 227

\bibitem[{{Simon} {et~al.}(2006{\natexlab{b}}){Simon}, {Rathborne}, {Shah},
  {Jackson}, \& {Chambers}}]{IRDCdistance}
{Simon}, R., {Rathborne}, J.~M., {Shah}, R.~Y., {Jackson}, J.~M., \&
  {Chambers}, E.~T. 2006{\natexlab{b}}, \apj, 653, 1325

\bibitem[{{Stark} \& {Lee}(2006)}]{stark06}
{Stark}, A.~A. \& {Lee}, Y. 2006, \apjl, 641, L113

\bibitem[{{Stil} {et~al.}(2006){Stil}, {Taylor}, {Dickey}, {Kavars}, {Martin},
  {Rothwell}, {Boothroyd}, {Lockman}, \& {McClure-Griffiths}}]{stil06}
{Stil}, J.~M. {et~al.} 2006, astro-ph/0605422

\bibitem[{{Testi} \& {Sargent}(1998)}]{Testi1998}
{Testi}, L. \& {Sargent}, A.~I. 1998, \apjl, 508, L91

\bibitem[{{van Dishoeck} \& {Blake}(1998)}]{vandishoeck98}
{van Dishoeck}, E.~F. \& {Blake}, G.~A. 1998, \araa, 36, 317

\bibitem[{{Williams} {et~al.}(2000){Williams}, {Blitz}, \&
  {McKee}}]{williams00}
{Williams}, J.~P., {Blitz}, L., \& {McKee}, C.~F. 2000, Protostars and Planets
  IV, 97

\bibitem[{{Young} {et~al.}(2006){Young}, {Enoch}, {Evans}, {Glenn}, {Sargent},
  {Huard}, {Aguirre}, {Golwala}, {Haig}, {Harvey}, {Laurent}, {Mauskopf}, \&
  {Sayers}}]{young06}
{Young}, K.~E. {et~al.} 2006, \apj, 644, 326

\end{thebibliography}

>>>>

% Get more information about latex package by using command   texdoc <packagename> , for example: texdoc rotating
% or visit this website: http://www.texdoc.net/   and search for the packagename
% Build procedure in texmaker 4.0.1 or texstudio 2.2 (svn):
% 1) press Tools:Clean within texmaker to delete old output files
% 2) press F11,F1,F11 and F1 within texmaker menu 
% to correctly compile this .tex file into a valid .PDF output file.
% use the Terminal command  "texdoc <packagename>" to get documentation about a specific tex package
% always save graphics files in .PDF format, not in .JPG or .PNG format
% The titling package offers features to create sophisticated title pages.
% The tocbibind package can automatically add bibliography, index, TOC, LOF, and LOT to the table
% of contents. It's even capable of using numbered headings instead of the default
% unnumbered ones.
% Use \citep{kennedy1998cationic}  for example when citing bibliography references in the .bib bibtex file

@@

The survey has detected approximately \ncoresapprox\ clumps over the
entire area to a limiting non-uniform 1-$\sigma$ noise level in the
range \bgpsdepthlow\ to \bgpsdepthhigh\ m\jyb\ in the inner Galaxy.
The BGPS source catalog is presented in a companion paper
\citep{kennedy1998cationic}.  This paper details the survey observations and
data reduction methods for the images.  We discuss in detail the
determination of astrometric and flux density calibration
uncertainties and compare our results to the literature.  Data
processing algorithms that separate astronomical signals from
time-variable atmospheric fluctuations in the data time-stream are
presented.  These algorithms reproduce the structure of the
astronomical sky over a limited range of angular scales and produce
artifacts in the vicinity of bright sources. Based on simulations, we
find that extended emission on scales larger than about 5\farcm9 is
nearly completely attenuated ($>90\%$) and the linear scale at which
the attenuation reaches 50\% is 3\farcm8.  Comparison with other
millimeter-wave data sets implies a possible systematic offset in flux
calibration, for which no cause has been discovered.

@@

\bibliographystyle{plainnat}
\bibliography{ms}
\cite{*}
